Hydra Battles and Cie

### 2021-01-20 doc/chapter-primrec.tex
restructuration of the Ackermann directory

\vspace{4pt}
\noindent
\emph{From\href{../theories/html/hydras.Ackermann.PrimRecExamples.html}{Ackermann.PrimRecExamples}}.
\begin{Coqsrc}
Require Import primRec.
Import extEqualNat.

@@

The constructors \texttt{zeroFunc}, \texttt{succFunc},  and \texttt{projFunc} of type
\texttt{PrimRec} allows us to write trivial proofs of primitive recursivity. 
Although  the following lemmas are alreday proven in 
\href{../theories/html/hydras.Ackermann.primRec.html}{Ackermann.primRec.v},
we wrote alternate proofs in 
\href{../theories/html/hydras.Ackermann.PrimRecExamples.html}%
{Ackermann.PrimRecExamples.v}, in order to illustrate the main proof patterns.

@@

\vspace{4pt}
\noindent
\emph{From \href{../theories/html/hydras.Ackermann.PrimRecExamples.html}{Ackermann.PrimRecExamples}}.
\begin{Coqsrc}
Lemma  const1_NIsPR n : isPR 0 n. 
Proof.
  induction n.
  - apply zeroIsPR.
  - destruct IHn as [x Hx].
   exists (composeFunc 0 1 (PRcons 0 0 x (PRnil 0)) succFunc). 
   cbn in *; intros; now rewrite Hx.
Qed.
\end{Coqsrc}

@@

The lemma \texttt{plusIsPR} is already proven in \href{../theories/html/hydras.Ackermann.primRec.html}{Ackermann.primRec}. We present in 
\href{../theories/html/hydras.Ackermann.PrimRecExamples.html}{Ackermann.PrimRecExamples}
a commented version of this proof,

@@

\begin{todo}
Comment more examples from   \href{../theories/html/hydras.Ackermann.PrimRecExamples.html}{Ackermann.PrimRecExamples}.
\end{todo}

>>>>

\vspace{4pt}
\noindent
\emph{From\href{../theories/html/hydras.Ackermann.MoreAck.PrimRecExamples.html}{Ackermann.MoreAck.PrimRecExamples}}.
\begin{Coqsrc}
Require Import primRec.
Import extEqualNat.

@@

The constructors \texttt{zeroFunc}, \texttt{succFunc},  and \texttt{projFunc} of type
\texttt{PrimRec} allows us to write trivial proofs of primitive recursivity. 
Although  the following lemmas are alreday proven in 
\href{../theories/html/hydras.Ackermann.primRec.html}{Ackermann.primRec.v},
we wrote alternate proofs in 
\href{../theories/html/hydras.Ackermann.MoreAck.PrimRecExamples.html}%
{Ackermann.MoreAck.PrimRecExamples.v}, in order to illustrate the main proof patterns.

@@

\vspace{4pt}
\noindent
\emph{From \href{../theories/html/hydras.Ackermann.MoreAck.PrimRecExamples.html}{Ackermann.MoreAck.PrimRecExamples}}.
\begin{Coqsrc}
Lemma  const1_NIsPR n : isPR 0 n. 
Proof.
  induction n.
  - apply zeroIsPR.
  - destruct IHn as [x Hx].
   exists (composeFunc 0 1 (PRcons 0 0 x (PRnil 0)) succFunc). 
   cbn in *; intros; now rewrite Hx.
Qed.
\end{Coqsrc}

@@

The lemma \texttt{plusIsPR} is already proven in \href{../theories/html/hydras.Ackermann.primRec.html}{Ackermann.primRec}. We present in 
\href{../theories/html/hydras.Ackermann.MoreAck.PrimRecExamples.html}{Ackermann.MoreAck.PrimRecExamples}
a commented version of this proof,

@@

\begin{todo}
Comment more examples from   \href{../theories/html/hydras.Ackermann.MoreAck.PrimRecExamples.html}{Ackermann.MoreAck.PrimRecExamples}.
\end{todo}
